Left-linear rules in adhesive categories

### 2024-02-09 icalp/fusione.tex
minori

\todo{P: qui probabilmente si puo' compattare tenendo solo cio' che si usa}
\todo{Si usa tutto per la classe B+ [DC]}
$\mathcal{M}$-adhesivity is well-behaved with respect to  the comma construction \cite{mac2013categories}, as shown by the following theorem.
\begin{theorem}[\cite{ehrig2006fundamentals,lack2005adhesive}]\label{lem:comma}
  Let $\A$ and $\B$ be respectively an $\mathcal{M}$-adhesive and an
  $\mathcal{M}'$-adhesive category. Let also $L:\A\rightarrow \C$ be a
  functor that preserves $\mathcal{M}$-pushouts, and
  $R:\B\rightarrow \C$ be a functor which preserves pullbacks.Then
  $\comma{L}{R}$ is $\cma{M}{M'}$-adhesive, where
  \[
    \cma{M}{M}':=\{(h,k)\in \mathcal{A}(\comma{L}{R}) \mid h\in
    \mathcal{M}, k\in \mathcal{M}'\}\]
\end{theorem}

In particular, we can apply this result to slices over and under a given object.

\begin{corollary}\label{cor:slice}
  Let $X$ be an object of an $\mathcal{M}$-adhesive category
  $\X$. Then $\X/X$ and $X/\X$ are, respectively, is $\mathcal{M}/X$-
  and $X/\mathcal{M}$-adhesive, where
  \[\mathcal{M}/X:=\{m\in \mathcal{A}(\X/X) \mid m\in \mathcal{M} \}
    \qquad X/\mathcal{M}:=\{m\in \mathcal{A}(X/\X) \mid m\in
    \mathcal{M} \}
  \]
\end{corollary}

@@

Often, we are interested in derivations only up to some notion of coherent isomorphism between them. This is done with the help of \Cref{rem:func}.

@@

\begin{definition}[switch equivalence]
  \label{de:switch-equivalence}
  Let $(\X, \R)$ be a left-linear DPO rewriting system.  Let
  $\der{D}, \der{E} : G \Mapsto H$ be derivations with the same
  length, $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and
  $\der{E}=\{\dder{E}_{i}\}_{i=0}^n$. If
  $\dder{D}_i \cdot \dder{D}_{i+1}$ is a switch of
  $\dder{E}_i \cdot \dder{E}_{i+1}$ for some $i \in [0,n-1]$ we write
  $\der{D} \leftrightsquigarrow_{(i,i+1)} \der{E}$. Then \emph{switch
    equivalence} is the least equivalence on derivation such that if
  $\der{D} \leftrightsquigarrow_{(i,i+1)} \der{E}$ then
  $\der{D} \equiv^s \der{E}$.
\end{definition}

@@

The fact that sequential indepedence implies switchability always
holds for linear rules. [REF] The result is so fundamental that it is
not even stated, in the sense that switchability is not introduced
axiomatically as in Definition~\ref{def:switch}, but it is based on
the explicit construction of a switch.

@@

\begin{definition}[Good independence pair]
  \label{def:filler}
  Let $(i_0, i_1)$ be an independence pair between two direct
  derivations $\dder{D}_0$, $\dder{D}_1$ in $(\X, \R)$ be a
  left-linear DPO rewriting system with $\X$ $\mathcal{M}$-adhesive,
  as in the solid part of the diagram below.
  \[
    \xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0
      \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} \ar@/^.20cm/@{.>}[ddrr]|(.7){u_0} & R_0
      \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0}
      && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
      \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} \ar@/_.20cm/@{.>}[ddll]|{u_1} && R_1 \ar[d]^{h_1} \\
      %
      G_0 &&
      \ar@{>->}[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1 &&
      \ar@{>->}[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2\\
      %
      & & & & P \ar@{>.>}[ull]^{p_0} \ar@{.>}[urr]_{p_1}
    }
  \]

  Consider the pullback of $g_0$ and $f_1$, getting $p_i : P \to D_i$
  ($i \in \{1,2\}$) and the mediating arrows $u_0\colon K_0\to P$ and
  $u_1\colon K_1\to P$ (dotted part of the diagram).
  %
  We will say that $(i_0, i_1)$ is a \emph{good independence pair} if
  the first and second square below are pushouts and if the third
  square exists and it is a pushout too.
  \[
    \xymatrix{
      %
      K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
      \ar@{>->}[r]^{l_1} \ar[d]_{u_1}& L_1 \ar[d]^{i_1}&K_1
      \ar[r]^{r_1} \ar[d]_{u_1}& R_1\ar@{.>}[d]^{j_0} \\
      %
      P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0&P \ar@{.>}[r]_{q_1} &
      Q_1}
  \]
\end{definition}

@@

We can now prove a version of the Local Church-Rosser Theorem for good independence pairs.

@@

[Proof~\ref{propEqui-proof}]

@@

\begin{definition}[node-merging graphical rewriting systems]
	\todo{sist di riscrittura grafico}
\end{definition}
\todo{esempi (no idea)}
\begin{lemma}
  All node-merging graphical rewriting systems are very tame.
  \todo{tutti very tame}
\end{lemma}

@@

The class of categories of type $\mathbb{B}$ is closed under the same constructions of \Cref{lem:comma,cor:slice,thm:functors}. This can be deduced at once from the fact that in such categories pullbacks and pushouts are computed componentwise.

\begin{lemma}\label{lem:closed} Let $\X$ be a category satisfying the $\mathcal{M}$-mixed and $\mathcal{M}$-pushout decomposition properties, then the following hold true:
	\begin{enumerate}
		\item   if $\Y$ is another category satisfying the $\mathcal{N}$-mixed and $\mathcal{N}$-pushout decomposition properties and $L:\X\rightarrow \A$ is a
		functor that preserves pushouts, and
		$R:\Y\rightarrow \A$ one preserving pullbacks.Then
		$\comma{L}{R}$ satisfies the $\cma{M}{N}$-mixed and the $\cma{M}{N}$-pushout decomposition properties, where
		\[
		\cma{M}{N}:=\{(h,k)\in \mor(\comma{L}{R}) \mid h\in
		\mathcal{M}, k\in \mathcal{N}\}\]
		\item  for every object $X$, $\X/X$ satisfies  the $\mathcal{M}/X$-mixed and the $\mathcal{M}/X$-pushout decomposition properties, while $X/\mathcal{M}$-adhesive satisfies their $X/\mathcal{M}$ variants, where
		\[\mathcal{M}/X:=\{m\in \mathcal{A}(\X/X) \mid m\in \mathcal{M} \}
		\qquad X/\mathcal{M}:=\{m\in \mathcal{A}(X/\X) \mid m\in
		\mathcal{M} \}
		\]
		\item  for every small
		category $\Y$, the category $\X^\Y$ satisfies the 
		$\mathcal{M}^{\Y}$-mixed and the $\mathcal{M}^{\Y}$-pushout decomposition properties , where
		\[\mathcal{M}^{\Y}:=\{\eta \in \mathcal{A}(\X^\Y) \mid \eta_Y \in
		\mathcal{M} \text{ for every } Y\in \Y\}\]
	\end{enumerate}
\end{lemma}

@@

\begin{definition}
	We will say that an $\mathcal{M}$-adhesive category $\X$ is of \emph{type $\mathbb{B}$} if:
	\begin{enumerate}
		\item every arrow in $\mathcal{M}$ is a coproduct coprojection;
		\item $\X$ has all pushouts;
		\item $\X$ has strict initial objects and, for every object $X$, the arrow $?_X\colon 0\to X $ belongs to $\mathcal{M}$;
		\item all pushouts are $\mathcal{M}$-stable.
	\end{enumerate}
\end{definition}

\begin{remark}
	It is worth to examine more closely conditions $1$ and $3$ of the above definition.
	\begin{itemize}
		\item Let $m_0\colon X_0 \rightarrowtail Y$ be an arrow in $\mathcal{M}$, the first condition means that there exists $m_1\colon X_1\to Y$, not necessarily in $\mathcal{M}$, such that $(Y, \{m_i\}_{i=0}^1)$ is a coproduct.
		\item $\X$ has strict initial objects if it has initial objects and every arrow $f:X\to 0$ is an isomorphism. Notice that if initial objects are strict, then $?_X\colon 0\to X$ is mono for every $X$: indeed for every pair $f,g\colon Y\rightrightarrows 0$ then, by strictness, $Y$ is initial and so $f=g$.
	\end{itemize}
\end{remark}

\begin{example}
	\todo{esempi}
\end{example}

\begin{example}
	\todo{esempi}
\end{example}

@@

We need a last technical results before proving that  an $\mathcal{M}$-adhesive category of type $\mathbb{B}$ satisfy the $\mathcal{M}$-mixed and $\mathcal{M}$-pushout decomposition properties.

\noindent
\parbox{10cm}{\begin{proposition}\label{prop:po2}
Let $\X$ be a category and suppose that $(X_0+X_1, \{\iota_{X_i}\}_{i=0}^1)$ and $(Y_0+Y_1, \{\iota_{Y_i}\}_{i=0}^1)$ are coproducts. Then for every $f\colon X_0\to Y_0$ the following are equivalent:
\begin{enumerate}
	\item the square on the right is a pushout;
	\item there exists an isomorphism $\phi\colon X_1\to Y_1$ such that $g=f+\phi$.
\end{enumerate}
\end{proposition}} \parbox{3cm}{$\xymatrix{X_0  \ar[r]^{f} \ar[d]_{\iota_{X_0}}& Y_0 \ar[d]^{\iota_{Y_0}}\\ X_0+X_1 \ar[r]_{g} & Y_0+Y_1}$}

@@

\noindent
\parbox{9.5cm}
{\begin{theoremEnd}[category=sec3]{proposition}\label{lem:cose}Let
    $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation, and suppose
    that $(i_0, i_1)$ is an independence pair between $\dder{D}_0$
    and $\der{D}_1$.  If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a
    switch of $\der{D}$ along $(i_0, i_1)$, then there exists
    $q_0\colon P\to D_{\der{E},0}$ in the diagram
    below \end{theoremEnd}}
\parbox{4cm}{$\xymatrix{D_{\der{E},0} \ar@{>->}[d]_{f_{\der{E},0}}&P
    \ar@{.>}[l]_{q_0} \ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1
    \ar@{>->}[d]^{f_1}\\ G_{0}&D_0 \ar@{>->}[l]^{f_0}\ar[r]_{g_0}&
    G_1}$}

@@

\begin{proposition}{proposition}
  \label{prop:tec}
  Let $(i_0, i_1)$ be an independence pair between two direct
  derivations $\dder{D}_0$ and $\dder{D}_1$ in a left-linear
  DPO rewriting system $(\X,\R)$. Consider the pullback of
  $f_1\colon D_1\mto G_1$ along $g_0\colon D_0\to G_1$ (first
  square below), then there exist the arrows
  $u_1\colon K_1\to P$ and $u_0\colon K_0\to P$ fitting in the
  central and right square. Moreover, the right one is always
  a pullback.
  \[\xymatrix{P \ar@{>->}[r]^{p_0} \ar[d]_{p_1} & D_0
      \ar[d]^{g_0}& K_0 \ar[r]^{r_0} \ar@{.>}[d]_{u_0}& R_0
      \ar[d]^{i_0} & K_1 \ar@{>->}[r]^{l_1} \ar@{.>}[d]_{u_1}&
      L_1 \ar[d]^{i_1}\\ D_1 \ar@{>->}[r]_{f_1} &G_1 &P
      \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0}
  \]
\end{proposition}

zzzzzzzzzzzzzzzz

>>>>

%\todo{P: qui probabilmente si puo' compattare tenendo solo cio' che si usa}
%\todo{Si usa tutto per la classe B+ [DC]}
%$\mathcal{M}$-adhesivity is well-behaved with respect to  the comma construction \cite{mac2013categories}, as shown by the following theorem.
%\begin{theorem}[\cite{ehrig2006fundamentals,lack2005adhesive}]\label{lem:comma}
  %Let $\A$ and $\B$ be respectively an $\mathcal{M}$-adhesive and an
  %$\mathcal{M}'$-adhesive category. Let also $L:\A\rightarrow \C$ be a
  %functor that preserves $\mathcal{M}$-pushouts, and
  %$R:\B\rightarrow \C$ be a functor which preserves pullbacks.Then
 % $\comma{L}{R}$ is $\cma{M}{M'}$-adhesive, where
  %\[
    %\cma{M}{M}':=\{(h,k)\in \mathcal{A}(\comma{L}{R}) \mid h\in
    %\mathcal{M}, k\in \mathcal{M}'\}\]
%\end{theorem}
$\mathcal{M}$-adhesivity is well-behaved with respect to  the construction of slice caregories, \cite{mac2013categories}, as shown by the following theorem.

\begin{theorem}\label{cor:slice}
  Let $X$ be an object of an $\mathcal{M}$-adhesive category
  $\X$. Then $\X/X$ and $X/\X$ are, respectively, is $\mathcal{M}/X$-
  and $X/\mathcal{M}$-adhesive, where
  \[\mathcal{M}/X:=\{m\in \mathcal{A}(\X/X) \mid m\in \mathcal{M} \}
    \qquad X/\mathcal{M}:=\{m\in \mathcal{A}(X/\X) \mid m\in
    \mathcal{M} \}
  \]
\end{theorem}

@@

Often, we are interested in derivations only up to some notion of coherent isomorphism between them. This leads us to the following definition.

@@

\begin{definition}[Switch equivalence]
  \label{de:switch-equivalence}
  Let $(\X, \R)$ be a left-linear DPO rewriting system.  Let
  $\der{D}, \der{E} : G \Mapsto H$ be derivations with the same
  length, $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and
  $\der{E}=\{\dder{E}_{i}\}_{i=0}^n$. If
  $\dder{D}_i \cdot \dder{D}_{i+1}$ is a switch of
  $\dder{E}_i \cdot \dder{E}_{i+1}$ for some $i \in [0,n-1]$ we write
  $\der{D} \leftrightsquigarrow_{(i,i+1)} \der{E}$. Then \emph{switch
    equivalence} is the least equivalence on derivation such that if
  $\der{D} \leftrightsquigarrow_{(i,i+1)} \der{E}$ then
  $\der{D} \equiv^s \der{E}$.
\end{definition}

@@

The fact that sequential indepedence implies switchability always
holds for linear rules (see \Cref{prop:equi}). The result is so fundamental that it is
not even stated, in the sense that switchability is not introduced
axiomatically as in Definition~\ref{def:switch}, but it is based on
the explicit construction of a switch.

@@

\begin{definition}[Good independence pair]
  \label{def:filler}
  Let $(i_0, i_1)$ be an independence pair between two direct
  derivations $\dder{D}_0$, $\dder{D}_1$ in $(\X, \R)$ be a
  left-linear DPO rewriting system with $\X$ $\mathcal{M}$-adhesive,
  as in the solid part of the diagram below.
  \[
    \xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0
      \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} \ar@/^.20cm/[ddrr]|(.3)\hole|(.55)\hole^(.7){u_0} & R_0
      \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0}
      && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
      \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} \ar@/_.20cm/[ddll]|(.3)\hole|(.55)\hole_(.7){u_1} && R_1 \ar[d]^{h_1} \\
      %
      G_0 &&
      \ar@{>->}[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1 &&
      \ar@{>->}[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2\\
      %
      & & & & P \ar@/^.3cm/@{>->}[ull]^{p_0} \ar@/_.3cm/[urr]_{p_1}
    }
  \]

  Consider the pullback of $g_0$ and $f_1$, getting $p_i : P \to D_i$
  ($i \in \{0,1\}$) and the arrows $u_0\colon K_0\to P$ and
  $u_1\colon K_1\to P$ given by \Cref{prop:tec} .
  %
  We will say that $(i_0, i_1)$ is a \emph{good independence pair} if
  the first and second square below are pushouts and if the third
  square exists and it is a pushout too.
  \[
    \xymatrix{
      %
      K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
      \ar@{>->}[r]^{l_1} \ar[d]_{u_1}& L_1 \ar[d]^{i_1}&K_1
      \ar[r]^{r_1} \ar[d]_{u_1}& R_1\ar@{.>}[d]^{j_0} \\
      %
      P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0&P \ar@{.>}[r]_{q_1} &
      Q_1}
  \]
\end{definition}

@@

We can now prove the Local Church-Rosser Theorem for good independence pairs.

@@

[Proof in \Cref{propEqui-proof}]

@@

\begin{definition}[Node-merging graphical rewriting systems]
	\todo{sist di riscrittura grafico}
\end{definition}
\todo{esempi (no idea)}
\begin{lemma}
  All node-merging graphical rewriting systems are very tame.
  \todo{tutti very tame}
\end{lemma}

@@

The class of categories of type $\mathbb{B}$ is closed under the same constructions of \Cref{cor:slice,thm:functors}. This can be deduced at once from the fact that in such categories pullbacks and pushouts are computed componentwise.

\begin{lemma}\label{lem:closed} Let $\X$ be a category satisfying the $\mathcal{M}$-mixed and $\mathcal{M}$-pushout decomposition properties, then the following hold true:
	\begin{enumerate}
		\item  for every object $X$, $\X/X$ satisfies  the $\mathcal{M}/X$-mixed and the $\mathcal{M}/X$-pushout decomposition properties, while $X/\mathcal{M}$-adhesive satisfies their $X/\mathcal{M}$ variants, where
		\[\mathcal{M}/X:=\{m\in \mathcal{A}(\X/X) \mid m\in \mathcal{M} \}
		\qquad X/\mathcal{M}:=\{m\in \mathcal{A}(X/\X) \mid m\in
		\mathcal{M} \}
		\]
		\item  for every small
		category $\Y$, the category $\X^\Y$ satisfies the 
		$\mathcal{M}^{\Y}$-mixed and the $\mathcal{M}^{\Y}$-pushout decomposition properties , where
		\[\mathcal{M}^{\Y}:=\{\eta \in \mathcal{A}(\X^\Y) \mid \eta_Y \in
		\mathcal{M} \text{ for every } Y\in \Y\}\]
	\end{enumerate}
\end{lemma}

@@

\begin{definition} 
	Let $\X$ be an  $\mathcal{M}$-adhesive category is of \emph{type $\mathbb{B}$} if:
	\begin{enumerate}
		\item every arrow in $\mathcal{M}$ is a coproduct coprojection;
		\item $\X$ has all pushouts;
		\item $\X$ has strict initial objects and, for every object $X$, the arrow $?_X\colon 0\to X $ belongs to $\mathcal{M}$;
		\item all pushouts are $\mathcal{M}$-stable.
	\end{enumerate}
\end{definition}

\begin{remark}
	It is worth to examine more closely conditions $1$ and $3$ of the above definition.
	\smallskip 
	\begin{itemize}
	\parbox{10cm}{\item Let $m_0\colon X_0 \rightarrowtail Y$ be an arrow in $\mathcal{M}$, the first condition means that there exists $m_1\colon X_1\to Y$ such that $(Y, \{m_i\}_{i=0}^1)$ is a coproduct. This, together with property $3$, entails that every coprojection in a coproduct is in $\mathcal{M}$. This follows sinc, any coproduct $(X_1+X_2, \{\iota_{X_i}\}_{i=0}^1)$ fits in a pushout diagram as the one aside.}
	  \parbox{3.5cm}{\vspace{-2.5em}$\xymatrix@C=25pt{0  \ar@{>->}[r]^-{?_{X_1}} \ar@{>->}[d]^{?_{X_2}}& X_1 \ar@{>->}[d]^{\iota_{X_1}}\\ X_2 \ar@{>->}[r]_-{\iota_{X_2}} & X_1+X_2}$}

	\smallskip 	\noindent 
	\parbox{13.5cm}{\item $\X$ has strict initial objects if it has initial objects and every arrow $f:X\to 0$ is an isomorphism. Notice that if initial objects are strict, then $?_X\colon 0\to X$ is mono for every $X$: indeed for every pair $f,g\colon Y\rightrightarrows 0$ then, by strictness, $Y$ is initial and so $f=g$.}
	\end{itemize} 
\end{remark}

\begin{example}
The category $\Set$ of sets and functions, with its class of monos, is of type $\mathbb{B}$. Similarly, the category $\textbf{Inj}$ of sets and injective functions is quasiadhesive and, with its class of regular monos, of type $\mathbb{B}$. 
\end{example}

@@

We need a last technical result before proving that  an $\mathcal{M}$-adhesive category of type $\mathbb{B}$ satisfy the $\mathcal{M}$-mixed and $\mathcal{M}$-pushout decomposition properties.

\noindent
\parbox{11cm}{\begin{proposition}\label{prop:po2}
Let $\X$ be an $\mathcal{M}$-adhesive category of type $\mathbb{B}$, and suppose that the square on the right is an $\mathcal{M}$ pullback. Then there exists $E\in \X$, $e\mto E\to C$ in $\mathcal{M}$ such that $(C, \{n, e\})$
\end{proposition}} \parbox{3cm}{$\xymatrix{A  \ar[r]^{f} \ar@{>->}[d]_{n}& B \ar@{>->}[d]^{m}\\ C\ar[r]_{g} & D}$}
\begin{proof}
	contenuto...
\end{proof}

@@

\begin{proposition}
	\label{prop:tec}
	Let $(i_0, i_1)$ be an independence pair between two direct
	derivations $\dder{D}_0$ and $\dder{D}_1$ in a left-linear
	DPO rewriting system $(\X,\R)$. Consider the pullback of
	$f_1\colon D_1\mto G_1$ along $g_0\colon D_0\to G_1$ (first
	square below), then there exist the arrows
	$u_1\colon K_1\to P$ and $u_0\colon K_0\to P$ fitting in the
	central and right square. Moreover, the right one is always
	a pullback.
	\[\xymatrix{P \ar@{>->}[r]^{p_0} \ar[d]_{p_1} & D_0
		\ar[d]^{g_0}& K_0 \ar[r]^{r_0} \ar@{.>}[d]_{u_0}& R_0
		\ar[d]^{i_0} & K_1 \ar@{>->}[r]^{l_1} \ar@{.>}[d]_{u_1}&
		L_1 \ar[d]^{i_1}\\ D_1 \ar@{>->}[r]_{f_1} &G_1 &P
		\ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0}
	\]
\end{proposition}

\noindent
\parbox{9.5cm}
{\begin{proposition}\label{lem:cose}Let
    $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation, and suppose
    that $(i_0, i_1)$ is an independence pair between $\dder{D}_0$
    and $\der{D}_1$.  If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a
    switch of $\der{D}$ along $(i_0, i_1)$, then there exists
    $q_0\colon P\to D_{\der{E},0}$ in the diagram
    below \end{proposition}}
\parbox{4cm}{$\xymatrix{D_{\der{E},0} \ar@{>->}[d]_{f_{\der{E},0}}&P
    \ar@{.>}[l]_{q_0} \ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1
    \ar@{>->}[d]^{f_1}\\ G_{0}&D_0 \ar@{>->}[l]^{f_0}\ar[r]_{g_0}&
    G_1}$}

@@
